\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-08-28 write_up/mixfishsim_ecolmod.tex
Updates to include more details in results

\replaced[id=PD]{Identifying}{Ensuring measures are implemented at} appropriate
spatial scales for fisheries closures has been a challenge in the past but
identified as crucial to its success \citep{Costello2010, Dunn2016}. Further,
poorly sited closures have led to ineffectual measures with unintended
consequences. For example, increased benthic impact on previously unexploited
areas was observed from the cod closure in the North Sea with a lack of
observed intended effect in reducing cod exploitation
\citep{Rijnsdorp2001,Dinmore2003}). \replaced[id=PD]{M}{Since then m}ore
refined spatiotemporal information has \added[id=PD]{since} become available
through the combination of logbook and Vessel Monitoring System (VMS) data
\citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more real-time
spatial management has been possible \citep[e.g.][]{Holmes2011}.  Such
information is, however, derived from an inherently biased sampling programme,
targeted fishing, where fishers establish favoured fishing grounds through an
explore-exploit strategy \citep{Bailey2018} where they search for areas with
high catches and then use experience to return to areas where they've
experienced high catch in the past.  \deleted[id=PD]{ Further, fishers
	generally only recorded landings (not catch) on a daily
	basis\todo{\added[id=JJ]{Its not clear what the problem is: landings
			collected on daily basis or landings recorded rather
			than catch}}.  This leads to questions about the
	validity of inference that can be drawn from landings data assigned to
	VMS activity pings.}\todo{\added[id=JJ]{This comes as a surprise: I
		thought this was going to be about
		discards}\added[id=PD]{Agree, have removed this to avoid
		confusion}}\\

@@

\replaced[id=PD]{A}{We developed and implemented a simulation model with a}
\replaced{simulation model that is modular and discrete-event based was
	developed. This approach enables efficient computation by allowing
	for}{approach, where} \added[id=PD]{sub-}modules \deleted[id=PD]{are}
implemented on time-scales appropriate to capture the characteristic of the
\replaced[id=PD]{different processes}{process modelled} (Figure 1).
\added[id=PD]{The following sub-modules were included to capture the full
	system: 1) Population dynamics, 2) Recruitment dynamics, 3) Population
	movement, 4) fishery dynamics.}\\

\deleted[id=PD]{The fishing model operated on a tow-by-tow basis, while}
\replaced[id=PD]{P}{p}opulation dynamics (fishing and natural mortality which
are instantaneous rates, growth of the population biomass) operate on a daily
time-step\replaced[id=PD]{, while p}{. P}opulation movement occurs on a weekly
time-step\replaced[id=PD]{. R}{, while r}ecruitment \replaced[id=PD]{takes
	place}{occurs} periodically each year for a set time
\replaced[id=PD]{duration}{period (e.g. 3 weeks)} specified for each
population\deleted[id=PD]{.}\added[id=PD]{, while the fishing module operates
	on a tow-by-tow basis (i.e. multiple events a day)}.
\deleted[id=PD]{Here we describe each of the model components; 1) Population
	dynamics, 2) Recruitment dynamics, 3) Population movement dynamics, 4)
	fishery dynamics.}

@@

The basic population level processes were simulated using a modified two-stage
Deriso-Schnute delay difference model which models the fish populations in
terms of aggregate biomass of recruits and mature components rather than
keeping track of individuals\citep{Deriso1980, Schnute1985, Dichmont2003}.
\added[id=PD]{A daily time-step was chosen to discretise continuous population
	processes on a biologically relevant and computationally tractable
	timescale.} \deleted[id=PD]{Here,}Population biomass growth and
depletion for pre-recruits and\deleted[id=PD]{fish} recruited
\added[id=PD]{fish}\deleted[id=PD]{to the fishery} were modelled separately as
a function of previous recruited biomass, intrinsic population growth and
recruitment functionally linked to the adult population size.  Biomass for each
cell $c$ was incremented each day $d$ as follows (the full parameter list is
detailed in Table \ref{tab: pop_variable}): 
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& (1 + \rho) B_{c,d} \cdot e^{-Z_{c,d}} - \rho \cdot e^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& (B_{c,d-1} \cdot e^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
	R_{\tilde{y}(c,y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be equal to $e^{-K}$ when $K$ is
the growth rate from a von Bertalanffy logistic growth model
\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{c,\tilde{y}}$ is the annual recruits in cell $c$ for year $y$. \\

Mortality $Z_{c,d}$ can be decomposed to natural mortality, $M_{c,d}$, and
fishing mortality, $F_{c,d}$, where both $M_{c,d}$ and $F_{c,d}$ are
instantaneous rates with $M_{c,d}$ fixed and $F_{c,d}$ calculated by solving
the Baranov catch equation \citep{Hilborn1992b} for $F_{c,d}$:
\begin{equation}
C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} * (1 - e^{-(F_{c,d} + M_{c,d})})
\cdot B_{c,d}
\end{equation}
where $C_{c,d}$ is the summed catch from the fishing model across all fleets
and vessels in cell $c$ for the population during the day $d$, and $B_{c,d}$
the daily biomass for the population in the cell. Here, catch and fishing
mortality are the sum of those across all fleets and vessels, where $F_{fl, v,
	c, d, p} = E_{fl, v, c, d} \cdot Q_{fl, p} \cdot D_{c, d, p}$ with
$fl$, $v$ and $p$ the fleet, vessel and population respectively and $E$ and $Q$
fishing effort and catchability of the gear, and $D$ is the density of the
population at the location fished. \todo{\added[id=CM]{[link $F$ to effort and
		catchability - as I think we have F as an emergent property of
		the fleets rather than something we solve for (I could be wrong
		though!) - catch for a vessel is a product of catchability and
		biomass, i.e. C = qB, but this catch is summed to solve for F.
		So its both really]}}\\

@@

Recruitment is modelled through a function relating the adult biomass to
recruits at time of recruitment. In \emph{MixFishSim}, it can be modelled
either either as a stochastic Beverton-Holt stock-recruit form
\citep{Beverton1957}: 
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & \frac{(\alpha \cdot S_{c,d})}{(\beta + S_{c,d})} \\
	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\sigma^2)]
	\end{split}
\end{equation}
Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
biomass (SSB) required to produce half the maximum stock size, $S$ current
stock size and $\sigma^2$ the variability in the recruitment due to stochastic
processes, or a stochastic Ricker form \citep{Ricker1954}:
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & B_{c,d} \cdot e^{(\alpha - \beta \cdot B_{c,d})} \\	
   	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
	\end{split}
\end{equation}
where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
dependent reduction in productivity as the SSB increases. In our example
application the Beverton-Holt form of stock recruit relationship was used for
all populations though either functional form can be chosen.

@@

To simulate \deleted[id=JJ]{how} fish population\deleted[id=JJ]{s might be}
distribut\replaced[id=JJ]{ion}{ed} in space and time\deleted[id=JJ]{, we
	employed} a Gaussian spatial process \added[id=JJ]{was employed} to
model habitat suitability for each of the populations on a 2d grid. JM: MENTION
IN THE INTRODUCTION \\

@@

\replaced[id=PD]{T}{In the simulation model, t}he habitat for each of the
populations \replaced[id=PD]{was}{is} generated \replaced[id=PD]{with}{through}
the \textit{RFSimulate} function of the \textit{RandomFields} R package
\citep{Schlater2015}, that simulates a Gaussian Random Field process given a
user defined error model and correlation structure. We define a stationary
habitat field and combine with a temporally dynamic thermal tolerance field to
imitate two key drivers of population dynamics. Each population
\replaced[id=PD]{was}{is} initialised at a single location, and subsequently
move\replaced[id=PD]{d}{s} according to a probabilistic
distrib\added[id=PD]{u}tion based on habitat suitability (represented by the
normalised values from the GRFs), temperature and distance
from current cell\replaced[id=PD]{:}{.} 
\begin{equation}
	Pr(J | I) = \frac{e^{-\lambda * d_{IJ}} \cdot
		(Hab_{J,p}^2 \cdot Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}e^{-\lambda * d} \cdot
		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
\end{equation}
Where $d_{IJ}$ is the euclidean distance between cell $I$ and cell $J$,
$\lambda$ is a given rate of decay, $Hab_{J,p}^2$ is the squared index of
habitat suitability for cell $J$ and population $p$, with $Tol_{J,p,wk}$ the
temperature tolerance for cell $J$ by population $p$ in week $wk$ (see
below).\\

During pre-defined weeks of the year the habitat suitability is modified with
\added[id=PD]{user-defined} spawning habitat locations\deleted[id=PD]{s},
\replaced[id=PD]{resulting in}{meaning} each population
\replaced[id=PD]{having}{has} concentrated areas where spawning takes place. In
the simulations the populations move\deleted[id=PD]{s} towards
\replaced[id=PD]{these cells}{this} in the weeks prior to spawning, resulting
in directional movement towards the spawning grounds.\todo{\added[id=JM]{What
		does it mean concisely? Areas are assigned?} \added[id=PD]{Yes,
		the areas are pre-defined - I have amended to reflect and tried
		to clarify}} \\ JM: WHAT ABOUT INDIVIDUAL INTERACTIONS:w

@@

For our implementation of a random walk directional change is based on a
negatively correlated circular distribution where a favourable fishing ground
is likely to be ``fished back over" by the vessel returning in the direction it
came from.  The step length (i.e. the distance travelled from the current to
the next fishing location) is determined by \deleted[id=JJ]{relating} recent
fishing success, measured as the summed value of fish caught (revenue, $Rev$),
\begin{equation}
Rev = \sum_{p=1}^{P} \replaced[id=PD]{L}{C}_{p} \cdot Pr_{p} 
\end{equation}
where $\replaced[id=PD]{L}{C}_{p}$ is \replaced[id=PD]{landings}{catch} of a
population $p$, and $Pr_{p}$ price of a population. Here, when fishing is
successful vessels remain in a similar location and continue to exploit the
local fishing grounds. When unsuccessful, they move some distance away from
the current fishing location.  The movement distance retains some degree of
stochasticity, that can be controlled separately, but is determined by the
relationship: 
\begin{equation}
	StepL = e^{log(\beta_{1}) + log(\beta_{2}) -
		(log(\frac{\beta_{1}}{\beta_{3}}))} * Rev
\end{equation}\todo{\added[id=JJ]{So
			step length increases with increasingly gross
			revenue?}\added[id=PD]{No, the opposite}}
Where $\beta_{1}$, $\beta_{2}$ and $\beta_{3}$ are parameters determining the
shape of the step function in its relation to revenue, so that, a step from
(x1,y1) to (x2, y2) is defined by:
\begin{equation}
	\begin{split}
 (x2, y2) =  & x1 + StepL \cdot \cos (\frac{\pi \cdot Br}{180}), \\
             & y1 + StepL \cdot \sin (\frac{\pi \cdot Br}{180}) \\	
 with  \hspace{0.5cm}     & Br_{t-1} < 180, Br_{t} = 180 + \sim vm[(0,360), k] \\
 			  & Br_{t-1} > 180, Br_{t} = 180 - \sim vm[(0,360), k] \\
	\end{split}
\end{equation}
where $k$ the concentration parameter from the von \replaced[id=JJ]{M}{m}ises
distribution that we correlate with the revenue so that $k = (Rev + 1 /
RefRev) * max_{k}$, where $max_{k}$ is the maximum concentration value, $k$,
and $RefRev$ is parametrised as for $\beta_{3}$ in the step length function. A
realised example of the step length and turning angle relationships to revenue
can be seen at Figure \ref{S-fig:15}.

@@

Where several fishing vessels exploit the same fish population competition is
known to play an important role in local distribution of fishing effort
\citep{Gillis1998}. If several vessels are fishing on the same patch of fish,
local depletion and interference \added[id=JJ]{competition} will affect fishing
location choice of the fleet as a whole \citep{Rijnsdorp2000, Poos2007a}. In
order to account for this behaviour, the fishing sub-model operates spatially
on a daily time-step so that for future days the biomass available to the
fishery is reduced in the areas fished. The cumulative effect is to make
heavily fished areas less attractive as a future fishing location choice as
reduced catch rates will be experienced. JM: INTERFERENCE COMPETITION COULD
ALSO BE REPRESENTED BY A LIMITATION FACTOR

@@

The following steps are undertaken to determine closures:
\todo{\added[id=JJ]{Procedure unclear. Refer to symbols in methods section or
		switch order starting with description of data type
		etc..}\added[id=PD]{Yes, will redo}}
\begin{enumerate}
	\item Extract data source
	\item Aggregate according to desired spatial and temporal resolution
	\item Interpolate across entire area at desired resolution using simple
		bivariate kriging using the \emph{interp} function from the R
		package akima \citep{Akima2006}. This is intended to represent
		a naive spatial model of catch rates, without knowledge of the
		spatial population dynamics.
	\item Close area covering top 5 \% of catch rates 
\end{enumerate}
In total 28 closure scenarios were run that represent combinations of:

@@

Figure \ref{fig:2} shows the consequences of different temporal aggregations of
the data over a ten-year period, with weekly (top), monthly (middle) and yearly
(bottom) catch compositions from across an aggregated 20 x 20 area. By
comparison to the 'real population', the monthly aggregation captures the major
patterns seen in the weekly data, albeit missing more subtle differences. The
yearly data assumes the same proportion of each population caught at any time
of the year due to the data aggregation. This assumption introduces
`aggregation bias' as the data may only be representative of some point (or no
point) in time. The commercial data on a weekly basis shows some of the same
patterns as the 'real population', though the first species (in red) is less
well represented and some weeks are missing catches from the area. The monthly
data shows some consistency between the 'real population' and commercial data
for species 2 - 4, though species 1 remains under-represented. On an annual
basis, interestingly the commercial data under represents the first species (in
red) while the survey over represents species 1. This is likely due to the
biases in commercial sampling, with the fisheries not targeting the areas where
species 1 are present and the survey sampling areas where species 1 is more
abundant than on average.

@@

From our simulations spatial disaggregation was more important than the
temporal disaggregation of the commercial data. This reflects the fact that
there was greater spatial heterogeneity over the spatial domain than
experienced in individual locations over the course of the year (Figure
\ref{fig:9}). This indicates that fixed closures, at the right resolution,
when based on commercially derived data have the potential to reduced fishing
mortality. The likely cost of poor spatial and temporal resolution is
associated with reduced effectiveness and potentially closing fishing
opportunities for other fisheries. \\

@@

>>>>

\replaced[id=PD]{Identifying}{Ensuring measures are implemented at} appropriate
spatial scales for fisheries closures has been a challenge in the past but
identified as crucial to its success \citep{Costello2010, Dunn2016}, and is
hampered where spatial information is coarse due to low resolution reporting of
fisheries catch which is subject to aggregation across larger gridded areas
\citep{Branch2005}. Further, coarse spatial data may lead to poorly sited closures,
which have led to ineffectual measures with unintended consequences.  For
example, increased benthic impact on previously unexploited areas was observed
from the cod closure in the North Sea with a lack of observed intended effect
in reducing cod exploitation \citep{Rijnsdorp2001,Dinmore2003}).
\replaced[id=PD]{M}{Since then m}ore refined spatiotemporal information has
\added[id=PD]{since} become available through the combination of logbook and
Vessel Monitoring System (VMS) data \citep{Lee2010, Bastardie2010,
	Gerritsen2012, Mateo2016} and more real-time spatial management has
been possible \citep[e.g.][]{Holmes2011}.  Such information is, however,
derived from an inherently biased sampling programme, targeted fishing, where
fishers establish favoured fishing grounds through an explore-exploit strategy
\citep{Bailey2018} where they search for areas with high catches and then use
experience to return to areas where they've experienced high catch in the past.
\deleted[id=PD]{ Further, fishers generally only recorded landings (not catch)
	on a daily basis\todo{\added[id=JJ]{Its not clear what the problem is:
			landings collected on daily basis or landings recorded
			rather than catch}}.  This leads to questions about the
	validity of inference that can be drawn from landings data assigned to
	VMS activity pings.}\todo{\added[id=JJ]{This comes as a surprise: I
		thought this was going to be about
		discards}\added[id=PD]{Agree, have removed this to avoid
		confusion}}\\

@@

\replaced[id=PD]{A}{We developed and implemented a fully spatially explicit
	simulation model with a} \replaced{simulation model that is modular and
	discrete-event based was developed. This approach enables efficient
	computation by allowing for}{approach, where}
\added[id=PD]{sub-}modules \deleted[id=PD]{are} implemented on time-scales
appropriate to capture the characteristic of the \replaced[id=PD]{different
	processes}{process modelled} (Figure 1).  \added[id=PD]{The following
	sub-modules were included to capture the full system: 1) Population
	dynamics, 2) Recruitment dynamics, 3) Population movement, 4) fishery
	dynamics.}\\

\deleted[id=PD]{The fishing model operated on a tow-by-tow basis, while}
\replaced[id=PD]{P}{p}opulation dynamics (including fishing and natural
mortality which are instantaneous rates, growth of the population biomass)
operate on a daily time-step\replaced[id=PD]{, while p}{. P}opulation movement
occurs on a weekly time-step\replaced[id=PD]{. R}{, while r}ecruitment
\replaced[id=PD]{takes place}{occurs} periodically each year for a set time
\replaced[id=PD]{duration}{period (e.g. 3 weeks)} specified for each
population\deleted[id=PD]{.}\added[id=PD]{, while the fishing module operates
	on a tow-by-tow basis (i.e. multiple events a day)}.
\deleted[id=PD]{Here we describe each of the model components; 1) Population
	dynamics, 2) Recruitment dynamics, 3) Population movement dynamics, 4)
	fishery dynamics.}

@@

The basic population level processes were simulated using a modified two-stage
Deriso-Schnute delay difference model which models the fish populations in
terms of aggregate biomass of recruits and mature components rather than
keeping track of individuals\citep{Deriso1980, Schnute1985, Dichmont2003}.
\added[id=PD]{A daily time-step was chosen to discretise continuous population
	processes on a biologically relevant and computationally tractable
	timescale.} \deleted[id=PD]{Here,}Population biomass growth was
modelled as a function of previous recruited biomass, intrinsic population
growth and recruitment functionally linked to the adult population size.
Biomass for each cell $c$ was incremented each day $d$ as follows (the full
parameter list is detailed in Table \ref{tab: pop_variable}): 
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& (1 + \rho) B_{c,d} \cdot \mathrm{e}^{-Z_{c,d}} - \rho \cdot
	\mathrm{e}^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& (B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
	R_{\tilde{y}(c,y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be equal to $\mathrm{e}^{-K}$ when $K$ is
the growth rate from a von Bertalanffy logistic growth model
\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{c,\tilde{y}}$ is the annual recruits in cell $c$ for year $y$. \\

Mortality $Z_{c,d}$ can be decomposed to natural mortality, $M_{c,d}$, and
fishing mortality, $F_{c,d}$, where both $M_{c,d}$ and $F_{c,d}$ are
instantaneous rates with $M_{c,d}$ fixed and $F_{c,d}$ calculated by solving
the Baranov catch equation \citep{Hilborn1992b} for $F_{c,d}$:
\begin{equation}
C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} * (1 - \mathrm{e}^{-(F_{c,d} + M_{c,d})})
\cdot B_{c,d}
\end{equation}
where $C_{c,d}$ is the summed catch from the fishing model across all fleets
and vessels in cell $c$ for the population during the day $d$, and $B_{c,d}$
the daily biomass for the population in the cell. Here, catch and fishing
mortality are the sum of those across all fleets and vessels, where $F_{fl, v,
	c, d, p} = E_{fl, v, c, d} \cdot Q_{fl, p} \cdot D_{c, d, p}$ with
$fl$, $v$ and $p$ the fleet, vessel and population respectively and $E$ and $Q$
fishing effort and catchability of the gear, and $D$ is the density of the
population at the location fished. \todo{\added[id=CM]{[link $F$ to effort and
		catchability - as I think we have F as an emergent property of
		the fleets rather than something we solve for (I could be wrong
		though!) - catch for a vessel is a product of catchability and
		biomass, i.e. C = qB, but this catch is summed to solve for F.
		So its both really]}}\\

@@

Recruitment is modelled through a function relating the adult biomass to
recruits at time of recruitment. In \emph{MixFishSim}, it can be modelled
either either as a stochastic Beverton-Holt stock-recruit form
\citep{Beverton1957}: 
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & \frac{(\alpha \cdot S_{c,d})}{(\beta + S_{c,d})} \\
	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\sigma^2)]
	\end{split}
\end{equation}
Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
biomass (SSB) required to produce half the maximum stock size, $S$ current
stock size and $\sigma^2$ the variability in the recruitment due to stochastic
processes, or a stochastic Ricker form \citep{Ricker1954}:
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & B_{c,d} \cdot \mathrm{e}^{(\alpha - \beta \cdot B_{c,d})} \\	
   	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
	\end{split}
\end{equation}
where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
dependent reduction in productivity as the SSB increases. In our example
application the Beverton-Holt form of stock recruit relationship was used for
all populations though either functional form can be chosen.

@@

To simulate \deleted[id=JJ]{how} fish population\deleted[id=JJ]{s might be}
distribut\replaced[id=JJ]{ion}{ed} in space and time\deleted[id=JJ]{, we
	employed} a Gaussian spatial process \added[id=JJ]{was employed} to
model habitat suitability for each of the populations on a 2d grid. \\

@@

\replaced[id=PD]{T}{In the simulation model, t}he habitat for each of the
populations \replaced[id=PD]{was}{is} generated \replaced[id=PD]{with}{through}
the \textit{RFSimulate} function of the \textit{RandomFields} R package
\citep{Schlater2015}, that simulates a Gaussian Random Field process given a
user defined error model and correlation structure. We define a stationary
habitat field and combine with a temporally dynamic thermal tolerance field to
imitate two key drivers of population dynamics. Each population
\replaced[id=PD]{was}{is} initialised at a single location, and subsequently
move\replaced[id=PD]{d}{s} according to a probabilistic
distrib\added[id=PD]{u}tion based on habitat suitability (represented by the
normalised values from the GRFs), temperature and distance
from current cell\replaced[id=PD]{:}{.} 
\begin{equation}
	Pr(J | I) = \frac{\mathrm{e}^{-\lambda * d_{IJ}} \cdot
		(Hab_{J,p}^2 \cdot
		Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}\mathrm{e}^{-\lambda * d} \cdot
		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
\end{equation}
Where $d_{IJ}$ is the euclidean distance between cell $I$ and cell $J$,
$\lambda$ is a given rate of decay, $Hab_{J,p}^2$ is the squared index of
habitat suitability for cell $J$ and population $p$, with $Tol_{J,p,wk}$ the
temperature tolerance for cell $J$ by population $p$ in week $wk$ (see
below).\\

During pre-defined weeks of the year the habitat suitability is modified with
\added[id=PD]{user-defined} spawning habitat locations\deleted[id=PD]{s},
\replaced[id=PD]{resulting in}{meaning} each population
\replaced[id=PD]{having}{has} concentrated areas where spawning takes place. In
the simulations the populations move\deleted[id=PD]{s} towards
\replaced[id=PD]{these cells}{this} in the weeks prior to spawning, resulting
in directional movement towards the spawning grounds.\todo{\added[id=JM]{What
		does it mean concisely? Areas are assigned?} \added[id=PD]{Yes,
		the areas are pre-defined - I have amended to reflect and tried
		to clarify}} \\

@@

For our implementation of a random walk directional change is based on a
negatively correlated circular distribution where a favourable fishing ground
is likely to be ``fished back over" by the vessel returning in the direction it
came from.  The step length (i.e. the distance travelled from the current to
the next fishing location) is determined by \deleted[id=JJ]{relating} recent
fishing success, measured as the summed value of fish caught (revenue, $Rev$),
\begin{equation}
Rev = \sum_{p=1}^{P} \replaced[id=PD]{L}{C}_{p} \cdot Pr_{p} 
\end{equation}
where $\replaced[id=PD]{L}{C}_{p}$ is \replaced[id=PD]{landings}{catch} of a
population $p$, and $Pr_{p}$ price of a population. Here, when fishing is
successful vessels remain in a similar location and continue to exploit the
local fishing grounds. When unsuccessful, they move some distance away from
the current fishing location.  The movement distance retains some degree of
stochasticity, that can be controlled separately, but is determined by the
relationship: 
\begin{equation}
	StepL = \mathrm{e}^{log(\beta_{1}) + log(\beta_{2}) -
		(log(\frac{\beta_{1}}{\beta_{3}}))} * Rev
\end{equation}\todo{\added[id=JJ]{So
			step length increases with increasingly gross
			revenue?}\added[id=PD]{No, the opposite}}
Where $\beta_{1}$, $\beta_{2}$ and $\beta_{3}$ are parameters determining the
shape of the step function in its relation to revenue, so that, a step from
(x1,y1) to (x2, y2) is defined by:
\begin{equation}
	\begin{split}
 (x2, y2) =  & x1 + StepL \cdot \cos (\frac{\pi \cdot Br}{180}), \\
             & y1 + StepL \cdot \sin (\frac{\pi \cdot Br}{180}) \\	
 with  \hspace{0.5cm}     & Br_{t-1} < 180, Br_{t} = 180 + \sim vm[(0,360), k] \\
 			  & Br_{t-1} > 180, Br_{t} = 180 - \sim vm[(0,360), k] \\
	\end{split}
\end{equation}
where $k$ the concentration parameter from the von \replaced[id=JJ]{M}{m}ises
distribution that we correlate with the revenue so that $k = (Rev + 1 /
RefRev) * max_{k}$, where $max_{k}$ is the maximum concentration value, $k$,
and $RefRev$ is parametrised as for $\beta_{3}$ in the step length function. A
realised example of the step length and turning angle relationships to revenue
can be seen at Figure \ref{S-fig:15}.

@@

Where several fishing vessels exploit the same fish population competition is
known to play an important role in local distribution of fishing effort
\citep{Gillis1998}. If several vessels are fishing on the same patch of fish,
local depletion and interference \added[id=JJ]{competition} will affect fishing
location choice of the fleet as a whole \citep{Rijnsdorp2000, Poos2007a}. In
order to account for this behaviour, the fishing sub-model operates spatially
on a daily time-step so that for future days the biomass available to the
fishery is reduced in the areas fished. The cumulative effect is to make
heavily fished areas less attractive as a future fishing location choice as
reduced catch rates will be experienced.

@@

The following steps are undertaken to determine closures:
\todo{\added[id=JJ]{Procedure unclear. Refer to symbols in methods section or
		switch order starting with description of data type
		etc..}\added[id=PD]{Yes, will redo}}
\begin{enumerate}
	\item Extract data source
	\item Aggregate according to desired spatial and temporal resolution
	\item Interpolate across entire area at desired resolution using simple
		bivariate interpolation using the \emph{interp} function from
		the R package akima \citep{Akima2006}. This is intended to
		represent a naive spatial model of catch rates, without
		knowledge of the spatial population dynamics.
	\item Close area covering top 5 \% of catch rates 
\end{enumerate}
In total 28 closure scenarios were run that represent combinations of:

@@

Figure \ref{fig:2} shows the consequences of different temporal aggregations of
the data over a ten-year period, with weekly (top), monthly (middle) and yearly
(bottom) catch compositions from across an aggregated 20 x 20 area. In the
'real population', the monthly aggregation captures the major patterns of
composition seen in the weekly data with similar mean and standard deviations.
In the weekly data species 1 = 9.36 (3.99), species 2 = 83.2 (5.60), species 3
= 3.57 (1.23), species 4 = 3.91 (1.59); in the monthly data species 1 = 9.23
(3.87), species 2 = 83.3 (5.52), species 3 = 3.62 (1.15), species 4 = 3.86
(1.52). While means were similar some of the variation was lost when aggregated
to an annual level; species 1 = 9.90 (0.173), species 2 = 82.2 (0.308), species
3 = 3.82 (0.119), species 4 = 4.03 (0.0502).\\

The commercial data on a weekly basis shows some of the same patterns as the
'real population', though the species 1 (in red) is less well represented and
some weeks are missing catches from the area. Here, weekly and monthly
compositions were nearly identical, with monthly composition of species 1 =
0.0472 (0.0139), species 2 = 94.4 (1.47), species 3 = 3.12 (1.47), species 4 =
2.40 (0.444). Again, yearly values head a similar mean but smaller standard
deviation.\\

The survey data was only available on an annual basis, and showed again a
slightly different composition; species 1 = 0.372 (0.00473), species 2 = 87.7
(0.193), species 3 = 0.729 (0.0200), species 4 = 11.2 (0.172).

@@

From our simulations spatial disaggregation was more important than the
temporal disaggregation of the commercial data. This reflects the fact that
there was greater spatial heterogeneity over the spatial domain than
experienced in individual locations over the course of the year (Figure
\ref{fig:9}). \\

The yearly data assumes the same proportion of each population caught at any
time of the year due to the data aggregation. This assumption introduces
`aggregation bias' as the data may only be representative of some point (or no
point) in time. The monthly data shows some consistency between the 'real population' and
commercial data for species 2 - 4, though species 1 remains under-represented.
On an annual basis, interestingly the commercial data under represents the
first species (in red) while the survey over represents species 1. This is
likely due to the biases in commercial sampling, with the fisheries not
targeting the areas where species 1 are present and the survey sampling areas
where species 1 is more abundant than on average. \\

This indicates that fixed closures, at the right resolution, when based on
commercially derived data have the potential to reduced fishing mortality. The
likely cost of poor spatial and temporal resolution is associated with reduced
effectiveness and potentially closing fishing opportunities for other
fisheries. \\

@@

\input{Temp_proportions.tex}
